Guided Proofreading of Automatic Segmentations for Connectomics

### 2016-11-16 paper/evaluation.tex
Latest.

\paragraph{CREMI A/B/C.} As part of the MICCAI 2016 challenge on circuit reconstruction from electron microscopy images (CREMI), six ssTEM datasets were made publicly available\footnote{\scriptsize{\url{http://www.cremi.org}}},  each $1250\times1250\times125$ voxels. Since only three datasets include manually-labeled `ground truth', we use these three volumes for our experiments. The volumes are part of an adult fruit fly (Drosophila melanogaster) brain. The resolution of all three datasets is $4\times4\times40~\text{nm}^3\text{/voxel}$.

>>>>

%\paragraph{CREMI A/B/C.} As part of the MICCAI 2016 challenge on circuit reconstruction from electron microscopy images (CREMI), six ssTEM datasets were made publicly available\footnote{\scriptsize{\url{http://www.cremi.org}}},  each $1250\times1250\times125$ voxels. Since only three datasets include manually-labeled `ground truth', we use these three volumes for our experiments. The volumes are part of an adult fruit fly (Drosophila melanogaster) brain. The resolution of all three datasets is $4\times4\times40~\text{nm}^3\text{/voxel}$.
